Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-06-11 Ben_Manuscripts/structure_paper/Draft.tex
More comments.

  %MRS7: this section reads a little bit as ``and then, and
  %then''. Think how to make it more focused on core ideas to communicate.

  There is a partition between the hydrophobic and hydrophilic regions, however
  it is a gradient in composition, rather than an abrupt division. The system
  does not confine sodium ions and head groups to just within the pore region.
  Based on size-exclusion experiments, we define the pore radius to be 0.6 nm
  %BJC5 : Add vertical line to plots for 'pore radius'? Might be too busy.
  ~\cite{zhou_supported_2005}. We see in all cases, that 19\% of sodium ions
  exist outside the pore region (except sandwiched, ordered basin, where 16\%
  are outside the pore). Additionally, we see that in all cases, about 3\% of the
  plotted tail density is located within the pore region (except ordered sandwiched,
  where 1.5\% are within the pore region). These observations bring into question how
  one should define a pore in these types of systems. One usually measures a 
  membrane's pore radius based on the size of a molecule it can reject, however
  it is not clear where the edges of the pores are and what size molecule would
  fit through. We leave these investigations for a future study.
  %MRS7: or could say that the size could be different depending on the the nature of the molecle. Could bring up
  %Sarah's results with different selectivity of molecules about the same size.

@@

  %MRS7: 
  In general, the composition of each region, particulary the pore region, is 
  similar between all systems. We believe we can solvate and study transport in any
  of the systems presented here and extract similar transport mechanisms. We will 
  need to verify that this assumption is true.

% BJC5 : I think this is making progress towards a better representation of these plots. I
% outlined the tops of the bars on the histograms so the individual rdf don't get covered.
% I think it helps. I also varied the thickness of the outlines so that the farthest back 
% line is thickest. That way, when the outlines overlap, you can see the ones in front.
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=1\linewidth]{sodium_density.png}
        \caption{Sodium Ions}
        \label{fig:sodium_regional_density}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=1\linewidth]{head_group_density.png}
        \caption{Head Groups}
        \label{fig:head_groups_regional_density}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=1\linewidth]{tails_density.png}
        \caption{Tails}
        \label{fig:tails_regional_density}
  \end{subfigure}
  \caption{In all cases, the component radial distribution functions exhibit a
	  composition gradient transitioning from the hydrophilic to the hydrophobic
	  regions. Systems with layers initially spaced 3.7 \AA~apart in the  parallel
	  displaced (a), and sandwiched (b) configurations both show the highest
	  concentrations of ions and head groups away from the pore center. Systems with
	  layers initially spaced 5 \AA~apart (c) and (d), both show the highest
	  concentrations of ions and head groups near the pore center, implying a more
	  uniform, disordered pore.}~\label{fig:overlaid_densities}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{pore_hbonds.png}
  \caption{}\label{fig:pore_hbonds}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{pore_hbonds_ft.png}
  \caption{}\label{fig:pore_hbonds_ft}
  \end{subfigure}
  \caption{(a) The average number of interlayer hydrogen bonds. Peaks indicate a 
  shared hydrogen bonded water molecule between a monomer head group and that stacked
  vertically above it. (b) }\label{fig:hbond_quantification}
  \end{figure}

@@

  We applied our crosslinking algorithm to equilibrated sandwiched and parallel
  displaced configurations in the ordered pore basin. We allowed the crosslinking
  algorithm to propagate until greater than 90 \% of vinyl groups were either involved
  in a crosslinking reaction or were terminated. See section S\ref{S-section:xlink}
  for further details on the crosslinking algorithm. We allowed the crosslinked
  configurations to simulate for 100 ns further in the NPT ensemble.

  % BJC5: Is it worth including the distance between layers and the correlation length?   
  There are minor changes to the physical characteristics of these systems when 
  they are crosslinked (See Figure ~\ref{fig:xlink}). The ionic conductivity of 
  the sandwiched configuration decreases while that of the parallel displaced 
  configuration stays the same. The pore spacing decreases in both systems by
  0.07 nm. The vertical monomer stacking distance increases in the sandwiched
  configuration and decreases in the parallel displaced configuration, however the 
  values of crosslinked configurations fall within uncertainty of their un-crosslinked
  counterparts. The correlation length decreases in both systems, but is most 
  pronounced in the parallel displaced system.

>>>>

  %MRS7: this section reads a little bit as ``and then, and
  %then''. Think how to make it more focused on core ideas to communicate. Thes is they are all about the same. Perhaps should be the beginning of the section?

  %MRS7: rephrase? Partition implies more abrupt.
  There is a partition between the hydrophobic and hydrophilic regions, however
  it is a gradient in composition, rather than an abrupt division. The system
  does not confine sodium ions and head groups to just within the pore region.
  Based on size-exclusion experiments, we define the pore radius to be 0.6 nm
  %BJC5 : Add vertical line to plots for 'pore radius'? Might be too busy.
  ~\cite{zhou_supported_2005}. We see in all cases, that 19\% of sodium ions
  exist outside the pore region (except sandwiched, ordered basin, where 16\%
  are outside the pore). Additionally, we see that in all cases, about 3\% of the
  plotted tail density is located within the pore region (except ordered sandwiched,
  where 1.5\% are within the pore region). These observations bring into question how
  one should define a pore in these types of systems. One usually measures a 
  membrane's pore radius based on the size of a molecule it can reject, however
  it is not clear where the edges of the pores are and what size molecule would
  fit through. We leave these investigations for a future study.
  %MRS7: or could say that the size could be different depending on the the nature of the molecle. Could bring up
  %Sarah's results with different selectivity of molecules about the same size.

@@

  In general, the composition of each region, particulary the pore region, is 
  similar between all systems. We believe we can solvate and study transport in any
  of the systems presented here and extract similar transport mechanisms. We will 
  need to verify that this assumption is true.

% BJC5 : I think this is making progress towards a better representation of these plots. I
% outlined the tops of the bars on the histograms so the individual rdf don't get covered.
% I think it helps. I also varied the thickness of the outlines so that the farthest back 
% line is thickest. That way, when the outlines overlap, you can see the ones in front.
%MRS7: looks weird, though - we should discuss more. Maybe just draw the tops of the histograms, and don't fill them in?
%MRS7: maybe do as three figures across?
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=1\linewidth]{sodium_density.png}
        \caption{Sodium Ions}
        \label{fig:sodium_regional_density}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=1\linewidth]{head_group_density.png}
        \caption{Head Groups}
        \label{fig:head_groups_regional_density}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=1\linewidth]{tails_density.png}
        \caption{Tails}
        \label{fig:tails_regional_density}
  \end{subfigure}
  %MRS7: lead with ``pretty much the same''
  \caption{In all cases, the component radial distribution functions exhibit a
	  composition gradient transitioning from the hydrophilic to the hydrophobic
	  regions. Systems with layers initially spaced 3.7 \AA~apart in the  parallel
	  displaced (a), and sandwiched (b) configurations both show the highest
	  concentrations of ions and head groups away from the pore center. Systems with
	  layers initially spaced 5 \AA~apart (c) and (d), both show the highest
	  concentrations of ions and head groups near the pore center, implying a more
	  uniform, disordered pore.}~\label{fig:overlaid_densities}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{pore_hbonds.png}
  \caption{}\label{fig:pore_hbonds}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{pore_hbonds_ft.png}
  \caption{}\label{fig:pore_hbonds_ft}
  \end{subfigure}
  %MRS7: add a bit more explanation - no description of discrete FT.
  \caption{(a) The average number of interlayer hydrogen bonds. Peaks indicate a 
  shared hydrogen bonded water molecule between a monomer head group and that stacked
  vertically above it. (b) }\label{fig:hbond_quantification}
  \end{figure}

@@

  We applied our crosslinking algorithm to equilibrated sandwiched and parallel
  displaced configurations in the ordered pore basin. We allowed the crosslinking
  algorithm to propagate until greater than 90\% of vinyl groups were either involved
  in a crosslinking reaction or were terminated. See section S\ref{S-section:xlink}
  for further details on the crosslinking algorithm. We allowed the crosslinked
  configurations to simulate for 100 ns further in the NPT ensemble.

  % BJC5: Is it worth including the distance between layers and the correlation length?   
  There are minor changes to the physical characteristics of these systems when 
  they are crosslinked (See Figure ~\ref{fig:xlink}). The ionic conductivity of 
  the sandwiched configuration decreases while that of the parallel displaced 
  configuration stays the same. The pore spacing decreases in both systems by
  0.07 nm. The vertical monomer stacking distance increases in the sandwiched
  configuration and decreases in the parallel displaced configuration, however the 
  values of crosslinked configurations fall within uncertainty of their un-crosslinked
  counterparts. The correlation length decreases in both systems, 
  %MRS7: from what to what?
but is most pronounced in the parallel displaced system.
